### 2018-12-13 tspl/instructions.tex
updated instructions

\item To download the exam paper, open a terminal window and 
type the following:
\begin{center}
   \texttt{getpapers}
\end{center}
This will create a subdirectory \texttt{tspl-pe} in your home directory,
containing the following files.
\begin{center}
\begin{tabular}{ll}
\texttt{tspl-pe/papers/exam.pdf}			& the exam \\
\texttt{tspl-pe/papers/instructions.pdf}		& these instructions \\
\texttt{tspl-pe/templates/Exam.lagda}			& exam template to edit \\
\texttt{tspl-pe/original\_templates/Exam.lagda}		& backup of exam template
\end{tabular}
\end{center}
The directories \texttt{tspl-pe/papers}, \texttt{tspl-pe/original\_templates} are
read only, but you may read and write \texttt{tspl-pe/templates}.

\item The textbook \emph{Programming Language Foundations in Agda} is available
by pointing your browser at:
\begin{center}
\texttt{file:///group/examreadonly/full/plfa/}
\end{center}
\item The Agda standard library is available by pointing your browser at:
\begin{center}
\texttt{file:///group/examreadonly/full/agda-stdlib/}
\end{center}
\item The Agda user manual is available by pointing your browser at:
\begin{center}
\texttt{file:///group/examreadonly/full/agda-docs/}
\end{center}
{\it (Note that internet access has been disabled.)}

>>>>

\item
  To download the exam paper, open a terminal window and type:
  \begin{center}
    \texttt{getpapers}
  \end{center}
  This will create a subdirectory \texttt{tspl-mpe} in your home directory,
  containing the following files.
  \begin{center}
    \begin{tabular}{ll}
      \texttt{tspl-mpe/papers/exam.pdf}                & the exam \\
      \texttt{tspl-mpe/papers/instructions.pdf}        & these instructions \\
      \texttt{tspl-mpe/templates/Exam.lagda}           & exam template to edit \\
      \texttt{tspl-mpe/original\_templates/Exam.lagda} & backup of exam template
    \end{tabular}
  \end{center}
  The directories \texttt{tspl-mpe/papers}, \texttt{tspl-mpe/original\_templates}
  are read only, but you may read and write \texttt{tspl-mpe/templates}.

\item
  To setup the Agda environment, open a second terminal window and type:
  and type:
  \begin{center}
    \texttt{tspl-setup}
  \end{center}
  This will open a browser, with three tabs which contain the textbook
  \emph{Programming Language Foundations in Agda}, the documentation for the
  Agda standard library, and the documentation for Agda.  (The browser may
  also attempt to link to the internet, which brings up a tab labeled
  ``Problem loading page''; this is expected and not a problem.)

{\it (Note that internet access has been disabled.)}
